Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-06-23 paper.qmd
Make paper camera-ready

Note: preprint now available here: https://osf.io/preprints/osf/a72yh

@@

</details>

@@

```{r alternative}
#| fig-cap: Hypothetical user stories for the CRUSE Tool illustrating that it can be used in different ways by different user groups.
#| label: fig-user-stories
# schematic = DiagrammeR::grViz("
# digraph {
#   # graph statement
#   #################
#   graph [rankdir = LR
#          color = white
#          fontsize = 36]

@@

The CRUSE Tool was developed for, and in close collaboration with, practitioners in the Republic of Ireland.
Although the overall approach of the project was quantitative, stakeholder feedback and qualitative data was deemed essential to ensure the tool was fit for purpose, mitigating against the risk that the project would be 'technocentric' and a 'problem looking for a solution'.
From the outset of the project, we aimed to follow @coppola2022's advocacy for a "human-centric approach in which personalization, purpose, ethics and inclusivity are key", rather than an 'off-the-shelf' product that failed to understand, let alone meet, local needs.
As outlined by @coppola2022, the 'digital transformation' taking place in transport planning (and many other sectors) has the potential to increase existing inequalities [@coppola2022].
A wide range of methods and measure can be taken to ensure that digital tools are accessible.

>>>>

<!-- Note: preprint now available here: https://osf.io/preprints/osf/a72yh

@@

</details> -->

@@

```{r alternative}
#| fig-cap: Hypothetical user stories for the CRUSE Tool illustrating that it can be used in different ways by different user groups.
#| label: fig-user-stories
#| out-width: 100%
# schematic = DiagrammeR::grViz("
# digraph {
#   # graph statement
#   #################
#   graph [rankdir = LR
#          color = white
#          fontsize = 36]

@@

The CRUSE Tool was developed for, and in close collaboration with, practitioners in the Republic of Ireland.
Although the overall approach of the project was quantitative, stakeholder feedback and qualitative data was deemed essential to ensure the tool was fit for purpose, mitigating against the risk that the project would be 'technocentric' and a 'problem looking for a solution'.
From the outset of the project, we aimed to follow a "human-centric approach in which personalization, purpose, ethics and inclusivity are key", rather than an 'off-the-shelf' product that failed to understand, let alone meet, local needs.
The 'digital transformation' taking place in transport planning (and many other sectors) has the potential to increase existing inequalities [@coppola2022].
A wide range of methods and measure can be taken to ensure that digital tools are accessible.

### 2024-06-23 paper.tex
Make paper camera-ready

\setstretch{2}
Note: preprint now available here: https://osf.io/preprints/osf/a72yh

Please cite as

Lovelace, Robin, Joey Talbot, Eugeni Vidal-Tortosa, Hussein Mahfouz,
Elaine Brick, Peter Wright, Gary O'Toole, et al.~2024. ``Cycle Route
Uptake and Scenario Estimation (CRUSE): An Approach for Developing
Strategic Cycle Network Planning Tools.'' OSF Preprints. March 29.
doi:10.31219/osf.io/a72yh.

This is an open and reproducible paper. See
\href{https://github.com/cruse-bike}{github.com/cruse-bike} for the code
and data used to generate the results presented here, and the code
underlying the web app hosted at \href{https://cruse.bike/}{cruse.bike}.

\newpage{}

@@

\includegraphics[width=3.31in,height=\textheight]{images/fig5.png}

@@

The CRUSE Tool was developed for, and in close collaboration with,
practitioners in the Republic of Ireland. Although the overall approach
of the project was quantitative, stakeholder feedback and qualitative
data was deemed essential to ensure the tool was fit for purpose,
mitigating against the risk that the project would be `technocentric'
and a `problem looking for a solution'. From the outset of the project,
we aimed to follow \citet{coppola2022}`s advocacy for a ``human-centric
approach in which personalization, purpose, ethics and inclusivity are
key'', rather than an 'off-the-shelf' product that failed to understand,
let alone meet, local needs. As outlined by \citet{coppola2022}, the
`digital transformation' taking place in transport planning (and many
other sectors) has the potential to increase existing inequalities
\citep{coppola2022}. A wide range of methods and measure can be taken to
ensure that digital tools are accessible.

>>>>

\setstretch{2}
\newpage{}

@@

\includegraphics[width=1\textwidth,height=\textheight]{images/fig5.png}

@@

The CRUSE Tool was developed for, and in close collaboration with,
practitioners in the Republic of Ireland. Although the overall approach
of the project was quantitative, stakeholder feedback and qualitative
data was deemed essential to ensure the tool was fit for purpose,
mitigating against the risk that the project would be `technocentric'
and a `problem looking for a solution'. From the outset of the project,
we aimed to follow a ``human-centric approach in which personalization,
purpose, ethics and inclusivity are key'', rather than an
`off-the-shelf' product that failed to understand, let alone meet, local
needs. The `digital transformation' taking place in transport planning
(and many other sectors) has the potential to increase existing
inequalities \citep{coppola2022}. A wide range of methods and measure
can be taken to ensure that digital tools are accessible.
